### 2014-07-22 writeups/code-deep-review.tex
First fit to full model code output, B field only
Modify model code to work with f2py, start testing Python f2py wrapper
code

@@

@@

% General solution, remarks
\subsubsection{General solutions -- some general notes}

For all solutions, $z(x) = x$ as we assume constant magnetic field (i.e., no
magnetic damping model here).

Additionally, the synchrotron cooling time constant $b = 1.57 \times 10^{-3}$
is defined as {\tt{a}} in Sean's code, to avoid conflict with magnetic field
$B$.

The distribution equations are near identical for $\mu > 1$ and $\mu < 1$,
but the limits are not the same.  Hence the distinct numerical implementations.

>>>>

Conclusion -- equate the loss and acceleration times as:
\[
    \tau_{\mt{accel}} \propto \frac{D}{v_s^2}
    \sim \frac{1}{b B^2 E} = \tau_{\mt{synch}}
\]
taking $D = \eta (C_D E_h / B) (E/E_h)^\mu$ as usual.
The scaling factors are correct, and the $\eta$ term indeed
should be $\eta E_h^{1-\mu}$, so that is correct.  The only weird part is
rederiving the prefactor, for which you must refer to several constants and
assumptions in Parizot et al. (2006); they treat spatial dependence and other
stuff in more detail.

So, for now, I shall trust Sean's judgement and just move forward with the
code.  In fact, it is the magnetic damping model that needs an extra factor of
$\eta^{-1/2}$ (and consequently Sean's equation (18) is also incorrect).

@@

\textbf{Not checked}: what is the role of $\alpha$ in all of this?!  Part of
the normalization and other factors above.  Low priority...

For all solutions, $z(x) = x$ as we assume constant magnetic field (i.e., no
magnetic damping model here).  The distribution equations are near identical
for $\mu > 1$ and $\mu < 1$, but the limits are not the same.  Hence the
distinct numerical implementations.
Additionally, the synchrotron cooling time constant $b = 1.57 \times 10^{-3}$
is defined as {\tt{a}} in Sean's code, to avoid conflict with magnetic field
$B$.

@@

### 2014-07-22 writeups/code-usage.tex
First fit to full model code output, B field only
Modify model code to work with f2py, start testing Python f2py wrapper
code

What do the parameters mean, or how do they affect predicted FWHM widths?
I still need to mess with this.  Roughly, per Sean's observations (to be
checked): $B_0$ controls overall FWHM widths, but doesn't affect width-energy
scaling much.  Diffusion parameters $\eta_2$ and $\mu$ are the main controls on
the width-energy scaling, as you might expect.

The effect of $\mu$ on width-energy scaling is shown in Figure 1.
The effects of both $\mu$ and $\eta_2 \sim D/D_{\mt{bohm}}$ on width-energy
scaling are shown in Figure 3.  Both decreasing $\mu$ and increasing $\eta_2$
will weaken the width-energy scaling, as the filaments are all smeared out by
diffusion, and smaller $\mu$ means diffusion is less sensitive to energy.

>>>>

What do the parameters mean, or how do they affect predicted FWHM widths?
I am still messing with this.  Roughly, per Sean's observations (to be
checked): $B_0$ controls overall FWHM widths, but doesn't affect width-energy
scaling much.  Diffusion parameters $\eta_2$ and $\mu$ are the main controls on
the width-energy scaling, as you might expect.

The effect of $\mu$ on width-energy scaling is shown in Figure 1.
The effects of both $\mu$ and $\eta_2 \sim D/D_{\mt{bohm}}$ on width-energy
scaling are shown in Figure 3.  Both increasing $\mu$ and increasing $\eta_2$
will weaken the width-energy scaling, as the filaments are all smeared out by
diffusion.  Larger $\mu$ means diffusion is stronger at higher energies, which
more strongly counteracts thinning with energy from synchrotron losses.

Finally, the effect of $\mu$ on width-energy scaling is stronger for larger
$\eta_2$ (Figure 3).  Figure 3 also suggests how degeneracy might occur --
e.g., multiple pairs of $\eta_2$, $\mu$ can reproduce $m_E = -0.15$, and we can
have strong variation in $\eta_2$ with just a small variation in $\mu$.  In
principle, the absolute widths should also help constrain the best set of
values, but it may simply not be a very strong constraint -- which we'll see
from $\Delta\chi^2 \leq 2.7$ errors, for example.
